---
title: "func_tests"
output: pdf_document
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE, warning=FALSE, message=F)
```

## Hyperband

### Classifiers jsons tidying up

```{r}
library(e1071)
library(randomForest)
#library(ipred)
library(jsonlite)
#library(rpart)
library(data.table)
library(caret)
library(ks)
#library(truncnorm)
#library(klaR)
library(tidyverse)
library(LiblineaR)
library(ranger)
source(file = "runClassifier.R")
#library(FNN)

files <- dir(path <- "~/school_stuff/schoolwork/witchcraft/inst/extdata/hyperband_jsons", pattern = "*.json")

names_clf <- files %>%
  map_chr(~ str_remove(.x, pattern = ".json"))

paths <- file.path(path, files)

jsons <- paths %>%
  map(.f = ~ fromJSON(txt = .x, flatten = T))

names(jsons) <- names_clf

```

### Hyperband itself

#### Initialization

```{r}

max_iter = 81

eta = 3

logeta = as_mapper(~ log(.x) / log(eta))

s_max = trunc(logeta(max_iter))

B = (s_max + 1) * max_iter

```

#### Inner loop

```{r}

calc_n_r = function(max_iter = 81, eta = 3, s = 4, B = 405) {
  
  n = trunc(ceiling(trunc(B/max_iter/(s+1)) * eta**s))
  
  r = max_iter * eta^(-s)
  
  ans = c(n, r)
  
  ans
  
}

nrs <- map_dfc(s_max:0, .f = ~ calc_n_r(max_iter, eta, .x, B)) %>%
  t() %>%
  `colnames<-`(value = c("n", "r")) %>%
  as_tibble()

nrs$s = s_max:0

```

#### Successive Halving First half

```{r}

calculate_ni_ri = function(x, eta = 3) {
  
  i = 0:(x$s)
  
  temp = as_mapper(~c(.x * eta^(-..1), .y * eta^..1))
  
  try = pmap(list(.x = x$n, .y = x$r, ..1 = i), .f = temp)
  
  try
  
}

calculate_ni_ri(x = nrs %>% slice(1))

```

#### Successive Halving Second Half

##### Run and return val loss

```{r}

# data_load <- read_csv(file = "~/witchcraft/inst/extdata/avila-tr.txt", col_names = F) %>%
#   rename(class = X11) %>%
#   mutate(class = as_factor(class))

data_load <- read_csv(file = "~/school_stuff/schoolwork/witchcraft/inst/extdata/schizo.csv") %>%
 mutate_at(.vars = vars(gain_ratio_1:gain_ratio_11),
           .funs = ~ as.numeric(.)) %>%
 mutate_if(is.character, as.factor)

#data_load <- mnist_raw <- read_csv("https://pjreddie.com/media/files/mnist_train.csv", col_names = FALSE)

#malware <- read_csv(file = "~/witchcraft/inst/extdata/test_malware_single.csv")

#malware$y <- "1"

#realware <- read_csv(file = "~/witchcraft/inst/extdata/test_realware_single.csv") 

#realware$y <- "0"

#preproc_model <- realware %>% bind_rows(malware)

#preproc_model <- data_load %>%
 # sample_frac(0.05) %>%
  #rename(y = X1) %>%
  #mutate(y = as_factor(y))

#preproc <- preproc_model %>% caret::preProcess(method = c("medianImpute", "center", "scale", "nzv", "corr"))

preproc <- data_load %>% caret::preProcess(method = c("medianImpute", "center", "scale", "zv", "corr"))

#preproc_dummies <- caret::dummyVars(~ . , data = preproc_model)

# data_model <- preproc_model %>%
#   dplyr::select(-class) %>%
#   predict(preproc, .) %>%
#   predict(dummyVars(~ ., data = ., drop2nd = T), .) %>%
#   as.data.frame() %>%
#   bind_cols(preproc_model %>% select(class)) %>%
#   select(-ID)

library(xgboost)
library(caret)

data_model <- data_load %>%
  dplyr::select(-class) %>%
  predict(dummyVars(~ ., data = ., drop2nd = T), .) %>%
  predict(preproc, .) %>%
  as.data.frame() %>%
  bind_cols(data_load %>% select(class))

split <- createDataPartition(data_model[, "class"], p = 0.75,
                             list = F)

data_train <- data_model[split, ]

data_test  <- data_model[-split, ]

data_model_train <- subset(data_train, select = -class)
data_model_train_dmat <- data_model_train %>% as.matrix()
mode(data_model_train_dmat) = 'double'
data_model_train_y <- subset(data_train, select = class) %>% as_vector()
data_model_train_y_dmat <- data_model_train_y %>% as.numeric() %>% map(.f = ~ .x - 1)

data_model_test <- subset(data_test, select = -class)
data_model_test_dmat <- data_model_test %>% as.matrix()
mode(data_model_test_dmat) = 'double'
data_model_test_y <- subset(data_test, select = class)

dmat <- xgb.DMatrix(data = data_model_train_dmat, label = data_model_train_y_dmat)

xgb_model <- xgboost(data = dmat,
                     nrounds = 5,
                     eta = 1,
                     objective = "multi:softprob",
                     num_class = length(unique(data_model_train_y)))

xg_pred_test <- predict(xgb_model, data_model_test_dmat)

pred_test <- matrix(xg_pred_test, ncol = length(unique(data_model_train_y)), byrow = T)

colnames(pred_test) = levels(data_load$class)

pred_test = apply(pred_test, 1, function(x) colnames(pred_test)[which.max(x)])

levels(pred_test) <- levels(data_load$class)

mean(data_model_test_y == pred_test)

default_params <- list(eta = -7, max_depth = 5, min_child_weight = 1, gamma = 0.01, colsample_bytree = 0.5)

source("runClassifier.R")

test_rpart <- runClassifier(data_train, data_test, params = list(minsplit = 5, maxdepth = 20, cp = -7, xval = 5), classifierAlgorithm = "rpart")
test_rf <- runClassifier(data_train, data_test, params = get_random_hp_config(jsons$randomForest), classifierAlgorithm = "randomForest")

testeeb_hb <- autoRlearn_(df = data_model, maxTime = 2, optimizationAlgorithm = "hyperband", bw = 3)

testeeb_bohb <- autoRlearn_(df = data_model, maxTime = 2, optimizationAlgorithm = "bohb", bw = 3)

#data_model <- predict(preproc, preproc_model)

# data_model <- preproc_model %>% 
#   predict(preproc, .) %>%
#   mutate(y = as_factor(y)) %>%
#   select(y, everything()) %>%
#   rename_if(is_numeric, .funs = ~ paste0("X", .x)) %>%
#   rename(y = Xy)

test_fast <- function(cost = 1, epsilon = 0.1, option = 5) {
  
liblinear <- LiblineaR::LiblineaR(data = data_model_train, target = data_model_train_y, cost = cost, epsilon = epsilon, type = option)

predlibli <- predict(liblinear, data_model_test)

predlibli
  
}

tic("HEHE")
smart_test <- SmartML::autoRLearn(maxTime = 5, directory = "~/witchcraft/inst/extdata/train_schizo.csv",
                                              testDirectory = "~/witchcraft/inst/extdata/test_schizo.csv",
                                 classCol = "y",
                                 nModels = 5,
                                 metric = 'avg-fscore')
toc()

testing_nb <- runClassifier(trainingSet = data_train,
              validationSet = data_test,
              params = list(laplace = 5), classifierAlgorithm = "naiveBayes", metric = 'acc')

feet <- fnb.train(x = data_train %>% select(-class), data_train[, "class"])

pred <- predict(feet, data_test %>% select(-class))

library(data.table)


params_cont <- function(param){

  type <- param$type

  type_scale <- param$scale

  if(type == "discrete") {

    param_estimation <- paste("'", base::sample(x = as.list(param$values), size = 1), "'", sep = "")

    param_estimation

  }

  else {

    param_estimation <- fcase(type_scale == "int", rdunif(1, a = as.numeric(param$minVal),
                                                          b = as.numeric(param$maxVal)),
                              type_scale == "any", runif(1,  min = as.numeric(param$minVal),
                                                         max = as.numeric(param$maxVal)),
                              type_scale == "double", runif(1,  min = as.numeric(param$minVal),
                                                            max = as.numeric(param$maxVal)),
                              type_scale == "exp", runif(1,  min = as.numeric(param$minVal),
                                                         max = as.numeric(param$maxVal)))

    param_estimation
  }

  param_estimation

}

get_random_hp_config <- function(params) {
  
  params_list <- params$params
  
  params_list_mapped <- map(.x = params_list,
                            .f = as_mapper( ~ params_cont(params[[.x]])))
  
  `names<-`(params_list_mapped, params_list)
  
} 

make_paste_final <- function(param) {
  
  params_list <- get_random_hp_config(jsons[[param]])
  
  names_list <- names(params_list) %>%
    map(~ str_glue(.x, " = ")) %>%
    map2(params_list, ~paste(.x, .y, sep = "")) %>%
    paste(collapse = ",")
  
  names_list
  
}

sample_n_params <- function(n, model) {
  
  #print(model)
  
  ans <- map_chr(.x = rep(model, n), .f = make_paste_final) %>%
    data.frame(model = model,
               params = .) %>%
    mutate_all(.funs = as.character)
  
  #print(ans)
  
  ans
  
}

make_fit <- function(train_df, model, params = "cp = 0.02") {
  
  paramsplit = length(str_split(params, pattern = ",") %>% as_vector())
      
  param = if (paramsplit > 1) {
    
    param_prep = params %>%
    str_split(pattern = ",") %>%
    flatten_chr()
  
    param_names = param_prep %>%
      map_chr(.f = ~ str_extract(string = .x, pattern = "[\\w=]*"))
  
    param_values = param_prep %>%
      map_dbl(.f = ~ parse_number(.x)) %>%
      `names<-`(value = param_names) %>%
      as.list()
    
    param_values
    
  } else {
    
    param_name = params %>%
      str_extract(pattern = "[\\w=]*")
    
    param_value = params %>%
      str_extract(pattern = "(?<==).*$") %>%
      str_trim() %>%
      as_vector(.type = "numeric") %>%
      `names<-`(value = param_name) %>%
      as.list()
    
    param_value
    
  }
  
  fit = function(model, train_df, ...) { eval(parse(text = model))(formula = y ~ ., data = train_df, ...) }
  
  fit_partial = partial(fit, model = model, train_df = train_df)
  
  ans = if (paramsplit > 1) { do.call(fit_partial, param) }
        else { do.call(fit_partial, param) }
  
  ans
  
}

#library(SmartML)

runklas <- runClassifier(data_train, data_test, params = get_random_hp_config(jsons$naiveBayes), classifierAlgorithm = "naiveBayes")

eval_loss <- function(model, train_df, test_df, params) {
  
  params_list <- eval(parse(text = paste("list(", params, ")")))
  
  pred <- runClassifier(trainingSet = train_df,
                        validationSet = test_df,
                        params = params_list,
                        classifierAlgorithm = model)$perf
  
}

# 
# data_train_y <- data_test %>% rename(y = class)
# 
# data_test_y <- data_test %>% rename(y = class)
# 
# test2 <- eval_loss(model = "randomForest", train_df = data_train_y, test_df = data_test_y, params = test$answer$params)

```

### Which models work:

```{r}

library(MASS)

testib_rpart <- eval_loss("rpart", train_df = data_train, test_df = data_test,
                    params = "xval = 10,maxdepth = 20, minsplit = 15,cp = 0.002")

testib_rf    <- eval_loss("randomForest", train_df = data_train, test_df = data_test,
                    params = "ntree = 195, mtry = 20,nodesize = 25")

testib_nb    <- eval_loss("naiveBayes", train_df = data_train, test_df = data_test,
                    params = "eps = 0.015, laplace = 1")

testib_bagging <- eval_loss("bagging", train_df = data_train, test_df = data_test,
                    params = "minsplit = 20, nbagg = 25, maxdepth = 30, cp = 0.1, xval = 1")

testib_fda     <- eval_loss("fda", train_df = data_train, test_df = data_test,
                    params = "dimension = 1, method = 'mars'")

testib_db      <- eval_loss("deepboost", train_df = data_train, test_df = data_test,
                    params = "num_iter = 10, tree_depth = 5, beta = 0.001, lambda = 0.1, loss_type = 'l'")


testib_lda     <- eval_loss("lda", train_df = data_train, test_df = data_test,
                    params = "tol = -2, method = 'mle'")

testib_c50 <- eval_loss("c50", train_df = data_train, test_df = data_test,
                    params = "trials = 5, rules = 'TRUE', earlyStopping = 'TRUE', CF = 0.002, fuzzyThreshold = 'FALSE', minCases = 5")

safe_loss <- safely(.f = eval_loss, otherwise = 0)

testib_rda     <- safe_loss("rda", train_df = data_train, test_df = data_test,
                            params = "lambda = 0, gamma = 0")

testib_knn  <- eval_loss("knn", train_df = data_train, test_df = data_test,
                            params = "k = 22")

testib_svm_radial <- eval_loss("svm", train_df = data_train, test_df = data_test,
                            params = "gamma = -4, cost = -2, tolerance = -10")


source("runClassifier.R")


library(SmartML)

smarttest <- SmartML::autoRLearn(maxTime = 15,
                                              directory = "~/witchcraft/inst/extdata/train_schizo.csv",
                                              testDirectory = "~/witchcraft/inst/extdata/test_schizo.csv",
                                  classCol = "y",
                                  nModels = 15)

```

### SuccessiveHalving

```{r}

source("runClassifier.R")

successive_halving <- function(df, i = 0, params_config, n, r, eta = 3, max_iter = 81, s_max = 4, evaluations = data.frame()) {
  
  if (i > s_max) {
    
    list("answer" = params_config, "sh_runs" = evaluations)
    
  } else {
    
    n_i = n * (eta ** -i)
    
    r_i = r * (eta ** i)
  
    r_p = r_i / max_iter
    
    #r_p = (80 / (s_max + 1)) * (i + 1)
  
    df_indexes = caret::createDataPartition(y = df$class,
                                            p = min(r_p, 0.8),
                                            list = F,
                                            times = 1)
  
    train_df = df[df_indexes, ] %>% as_tibble()
  
    test_df = df[-df_indexes, ] %>% as_tibble()
  
    configs = params_config
  
    model_list = configs$model %>% as.character()

    params_list = configs$params %>% as.character()

     # partial_eval = possibly(.f = partial(.f = eval_loss,
     #                         train_df = train_df,
     #                         test_df = test_df), otherwise = 0)
     # 
    partial_eval = partial(.f = eval_loss,
                           train_df = train_df,
                           test_df = test_df)
    

    test_sample = map2(.x = model_list,
                       .y = params_list,
                       .f = partial_eval)
  
    configs$acc = test_sample
  
    final_df = configs %>%
      as_tibble() %>%
      mutate(acc = round(as.numeric(acc), 4)) %>%
      arrange(desc(acc)) %>%
      mutate_all(.funs = as.character()) %>%
      mutate(budget = r_i,
             rp = r_p)
    
    #cat('Stage: ', i, ' of SH ', 'results: \n', sep = "")
    
   # print(final_df)
    
  
    
    successive_halving(df = df,
                       i = i + 1,
                       params_config = final_df %>% head(n_i),
                       n = n,
                       r = r,
                       eta = eta,
                       max_iter = max_iter,
                       s_max = s_max,
                       evaluations = evaluations %>% bind_rows(final_df)) 
  }
  
  }
 
test <- successive_halving(df = data_model, params_config = sample_n_params(n = 81, model = "boosting"), n = 81, r = 1)

```

## Successive Ressampling Code

```{r}

library(ks)
library(truncnorm)
library(KernSmooth)

  EI <- function(..., lkde, gkde) { predict(lkde, x = c(...)) / predict(gkde, x = c(...)) }

  
  f2 <- function(df) {
    do.call("mapply", c(list, df, SIMPLIFY = FALSE, USE.NAMES=FALSE))
  }
  
  coalesce_all_columns <- function(df, group_vars = NULL) {
      
      if (is.null(group_vars)) {
          group_vars <- 
              df %>%
              purrr::keep(~ dplyr::n_distinct(.x) == 1L) %>% 
              names()
      }
      
      msk <- colnames(df) %in% group_vars
      same_df <- df[1L, msk, drop = FALSE]
      coal_df <- df[, !msk, drop = FALSE] %>%
          purrr::map_dfc(na.omit)
      
      cbind(same_df, coal_df)
  }
  
  #profvis(expr = {
  
  
  samples_filtered <- test$sh_runs
  
  mdl <- samples_filtered$model[[1]]
  
  params_list <- jsons[[mdl]]$params

  length_params <- length(params_list)
  
  biggest_budget_that_satisfies <- samples_filtered %>%
    arrange(desc(budget), desc(acc)) %>%
    group_by(budget) %>%
    mutate(size = n()) %>%
    ungroup() %>%
    filter(size > length_params * 20/3) %>%
    filter(budget == max(budget)) %>%
    select(-size) %>%
    separate(col = params,
             into = jsons[[mdl]]$params,
             sep = ",") %>%
    select(-model, -rp) %>%
    mutate_if(is.character, parse_number)
  
  l_samples <- biggest_budget_that_satisfies %>% top_frac(0.15, wt = acc) %>% select(-acc, -budget)
  
  g_samples <- biggest_budget_that_satisfies %>% top_frac(-0.85, wt = acc) %>% select(-acc,
                                                                                      -budget)

  # l_kde <- kde(l_samples, binned = FALSE)
  # 
  # g_kde <- kde(g_samples)
  # 
  l_kde_bws <- map_dbl(l_samples, dpik, scalest = "stdev")
  
  g_kde_bws <- map_dbl(g_samples, dpik, scalest = "stdev")
  
  ###
  
  l_kde_means <- map2_dbl(.x = l_samples, .y = l_kde_bws, .f = ~ mean(bkde(x = .x, bandwidth = .y)$x))
    
  g_kde_means <- map2_dbl(.x = g_samples, .y = g_kde_bws, .f = ~ mean(bkde(x = .x, bandwidth = .y)$x))
  
  ## trunc
  
  maxvals <- map_dbl(.x = params_list, .f = ~ readr::parse_number(jsons[[mdl]][[.x]]$maxVal))
  
  minvals <- map_dbl(.x = params_list, .f = ~ readr::parse_number(jsons[[mdl]][[.x]]$minVal)) 
  
  types   <- map_chr(.x = params_list, .f = ~ jsons[[mdl]][[.x]]$scale)
  
  partial_rtruncnorm <- function(n, a, b, mu, sigma, type) {
    
    case_when(type == "int"    ~ round(rtruncnorm(n = n, a = a, b = b, mean = mu, sd = sigma)),
              type == "double" | type == "exp" ~ rtruncnorm(n = n, a = a, b = b, mean = mu, sd = sigma))
    
  }
  
   partial_dtruncnorm <- function(x, a, b, mu, sigma) {
    
    dtruncnorm(x = x, a = a, b = b, mean = mu, sd = sigma)
    
   }
   
  # open_convolve <- function(x, y, type = "open") { convolve(x, y, type = type) }

  batch_samples <- pmap_dfc(.l = list("a" = minvals,
                                      "b" = maxvals,
                                      "mu" = l_kde_means,
                                      "sigma" = l_kde_bws,
                                      "type" = types),
                            .f = partial_rtruncnorm,
                            n = 81) %>%
    set_names(nm = params_list)
  
  batch_samples_densities_l <- pmap_dfc(.l = list("x" = batch_samples,
                                                  "a" = minvals,
                                                  "b" = maxvals,
                                                  "mu" = l_kde_means,
                                                  "sigma" = l_kde_bws),
                            .f = partial_dtruncnorm)
  
  # %>%
    #reduce(`*`)
  
  batch_samples_densities_g <- pmap_dfc(.l = list("x" = batch_samples,
                                                  "a" = minvals,
                                                  "b" = maxvals,
                                                  "mu" = g_kde_means,
                                                  "sigma" = g_kde_bws),
                            .f = partial_dtruncnorm)
  
  
  
  # %>%
    #reduce(`*`)
  
  evaluate_batch_convolution <- batch_samples_densities_l / batch_samples_densities_g
  
  rank_sample_density <- function(samp, kdensity, n) {
    
    samp <- samp %>% as.data.frame()
    
    samp$rank <- kdensity
    
    sorted_samp <- samp %>% arrange(desc(rank)) %>% head(n)
    
    subset(sorted_samp, select = -rank)
    
  }
  
  #rsd <- rank_sample_density(samp = bs$., kdensity = bs$rank, n = 27)
  
  #bs$rank <- evaluate_batch_convolution$V1
  
  #bs <- batch_samples$V1 %>% as.data.frame()
  
  
  #individual_sort <- bs %>% top_n(n = 27, wt = rank)
    
  #evaluate_batch <- pmap(.l = batch_samples, .f = EI, lkde = l_kde, gkde = g_kde) %>% as_vector()
  
  #batch_samples$EI <- evaluate_batch 
  
  #batch_samples$eEI <- evaluate_batch_convolution
  
  
  mega_test <- map2_dfc(.x = batch_samples, .y = evaluate_batch_convolution, .f = rank_sample_density, n = 27)
  
  colnames(mega_test) <- params_list
  
  braaduts <- mega_test %>%
    gather(key, value) %>%
    mutate(params = paste(key, value, sep = " = ")) %>%
    .[["params"]] %>%
    matrix(nrow = 27, ncol = 5) %>%
    as.data.frame() %>%
    unite(col = "params", sep = ",") %>%
    mutate(model = mdl)
    
  
  #})


sh_tss <- successive_halving(df = data_model, params_config = braaduts, n = 81, r = 1)

```

## Successive Resampling final

```{r}

  EI <- function(..., lkde, gkde) { predict(lkde, x = c(...)) / predict(gkde, x = c(...)) }

  
  f2 <- function(df) {
    do.call("mapply", c(list, df, SIMPLIFY = FALSE, USE.NAMES=FALSE))
  }
  
  coalesce_all_columns <- function(df, group_vars = NULL) {
      
      if (is.null(group_vars)) {
          group_vars <- 
              df %>%
              purrr::keep(~ dplyr::n_distinct(.x) == 1L) %>% 
              names()
      }
      
      msk <- colnames(df) %in% group_vars
      same_df <- df[1L, msk, drop = FALSE]
      coal_df <- df[, !msk, drop = FALSE] %>%
          purrr::map_dfc(na.omit)
      
      cbind(same_df, coal_df)
  }
  dpikSafe <- function(x, ...)
  {
	result <- try(dpik(x, ...), silent = TRUE)

	if (class(result) == "try-error")
	{
		msg <- geterrmessage()
		if (grepl("scale estimate is zero for input data", msg))
		{
			warning("Using standard deviation as scale estimate, probably because IQR == 0")
			result <- try(dpik(x, scalest = "stdev", ...), silent = TRUE	)
			
			if (class(result) == "try-error") {
			  
			  msg <- geterrmessage()
			  if (grepl("scale estimate is zero for input data", msg)) {
			    
			    warning("0 scale, bandwidth estimation failed. using 1e-3")
			    result <- 1e-3
			    
			  }
			  
			}
			
		} else 
		{
			stop(msg)
		}		
		
	}
	return(result)
  }
  

successive_resampling <- function(df, samples = 64, n = 27, bw = 1.5) {
  
  samples_filtered <- df
  
  mdl <- samples_filtered$model[[1]]
  
  params_list <- jsons[[mdl]]$params

  length_params <- length(params_list)
  
  biggest_budget_that_satisfies <- samples_filtered %>%
    arrange(desc(budget), desc(acc)) %>%
    group_by(budget) %>%
    mutate(size = n()) %>%
    ungroup() %>%
    filter(size > length_params * 20/3) %>%
    filter(budget == max(budget)) %>%
    select(-size) %>%
    separate(col = params,
             into = jsons[[mdl]]$params,
             sep = ",") %>%
    select(-model, -rp) %>%
    mutate_if(is.character, parse_number)
  
  l_samples <- biggest_budget_that_satisfies %>% top_frac(0.15, wt = acc) %>% select(-acc, -budget)
  
  g_samples <- biggest_budget_that_satisfies %>% top_frac(-0.85, wt = acc) %>% select(-acc,
                                                                                      -budget)

  l_kde_bws <- map_dbl(l_samples, dpikSafe)
  
  g_kde_bws <- map_dbl(g_samples, dpikSafe)
  
  l_kde_means <- map2_dbl(.x = l_samples, .y = l_kde_bws, .f = ~ mean(bkde(x = .x, bandwidth = .y)$x))
    
  g_kde_means <- map2_dbl(.x = g_samples, .y = g_kde_bws, .f = ~ mean(bkde(x = .x, bandwidth = .y)$x))
  
  maxvals <- map_dbl(.x = params_list, .f = ~ readr::parse_number(jsons[[mdl]][[.x]]$maxVal))
  
  minvals <- map_dbl(.x = params_list, .f = ~ readr::parse_number(jsons[[mdl]][[.x]]$minVal)) 
  
  types   <- map_chr(.x = params_list, .f = ~ jsons[[mdl]][[.x]]$scale)
  
  partial_rtruncnorm <- function(n, a, b, mu, sigma, type) {
    
    case_when(type == "int"    ~ round(rtruncnorm(n = n, a = a, b = b, mean = mu, sd = sigma)),
              type == "double" | type == "exp" ~ rtruncnorm(n = n, a = a, b = b, mean = mu, sd = sigma))
    
  }
  
   partial_dtruncnorm <- function(x, a, b, mu, sigma) {
    
    dtruncnorm(x = x, a = a, b = b, mean = mu, sd = sigma)
    
   }

  batch_samples <- pmap_dfc(.l = list("a" = minvals,
                                      "b" = maxvals,
                                      "mu" = l_kde_means,
                                      "sigma" = l_kde_bws,
                                      "type" = types),
                            .f = partial_rtruncnorm,
                            n = samples) %>%
  set_names(nm = params_list)
  
  batch_samples_densities_l <- pmap_dfc(.l = list("x" = batch_samples,
                                                  "a" = minvals,
                                                  "b" = maxvals,
                                                  "mu" = l_kde_means,
                                                  "sigma" = l_kde_bws),
                            .f = partial_dtruncnorm)
  
  batch_samples_densities_g <- pmap_dfc(.l = list("x" = batch_samples,
                                                  "a" = minvals,
                                                  "b" = maxvals,
                                                  "mu" = g_kde_means,
                                                  "sigma" = g_kde_bws),
                            .f = partial_dtruncnorm)
  
  evaluate_batch_convolution <- batch_samples_densities_l / batch_samples_densities_g
  
  rank_sample_density <- function(samp, kdensity, n) {
    
    samp <- samp %>% as.data.frame()
    
    samp$rank <- kdensity
    
    sorted_samp <- samp %>% arrange(desc(rank)) %>% head(n)
    
    subset(sorted_samp, select = -rank)
    
  }
  
  mega_test <- map2_dfc(.x = batch_samples, .y = evaluate_batch_convolution, .f = rank_sample_density, n = n)
  
  colnames(mega_test) <- params_list
  
  braaduts <- mega_test %>%
    gather(key, value) %>%
    mutate(params = paste(key, value, sep = " = ")) %>%
    .[["params"]] %>%
    matrix(nrow = n, ncol = length(params_list)) %>%
    as.data.frame() %>%
    unite(col = "params", sep = ",") %>%
    mutate(model = mdl) %>%
    select(model, params)
  
}

succ_samp <- successive_resampling(df = test$sh_runs)


```

### Hyperband, without bayesian opt

```{r}

hyperband <- function(df, model, max_iter = 81, eta = 3) {

  logeta = as_mapper(~ log(.x) / log(eta))

  s_max = trunc(logeta(max_iter))

  B = (s_max + 1) * max_iter

  nrs = map_dfc(s_max:0, .f = ~ calc_n_r(max_iter, eta, .x, B)) %>%
    t() %>%
    `colnames<-`(value = c("n", "r")) %>%
    as_tibble()

  nrs$s = s_max:0
  
  partial_halving <- function(n, r, s) {
    
    successive_halving(df = df,
                       params_config = sample_n_params(n = n, model = model),
                       n = n,
                       r = r,
                       s_max = s,
                       max_iter = max_iter,
                       eta = eta)
    
  }
  
  pmap(.l = nrs,
       .f = partial_halving)

}

test_hb <- hyperband(df = data_model, model = "boosting") %>% map_dfr(.f = ~ .x[["answer"]])

```

### Hyperband, with bayesian opt but soft.

```{r}

bohb_soft <- function(df, model, max_iter = 81, eta = 3) {

  logeta = as_mapper(~ log(.x) / log(eta))

  s_max = trunc(logeta(max_iter))

  B = (s_max + 1) * max_iter

  nrs = map_dfc(s_max:0, .f = ~ calc_n_r(max_iter, eta, .x, B)) %>%
    t() %>%
    `colnames<-`(value = c("n", "r")) %>%
    as_tibble()

  nrs$s = s_max:0
  
  random_sh = successive_halving(df = df,
                                 params_config = sample_n_params(n = as.numeric(nrs[1, 1]), model = model),
                                 n = as.numeric(nrs[1, 1]),
                                 r = as.numeric(nrs[1, 2]),
                                 s_max = as.numeric(nrs[1, 3]),
                                 max_iter = max_iter,
                                 eta = eta)
  
  liszt = vector(mode = "list",
                 length = max(nrs$s) + 1)
  
  liszt[[1]] <- random_sh
  
  for (row in 2:nrow(nrs)) {
    
    cat(' \n got here \n')
    
    bayesian_opt_samples = successive_resampling(df = liszt[[row - 1]]$sh_runs,
                                                 samples = 256,
                                                 n = nrs[[row, 1]] * 0.85,
                                                 bw = 3)
    
    print(bayesian_opt_samples)
    
    liszt[[row]] <- successive_halving(df = df,
                                       params_config = bayesian_opt_samples %>% bind_rows(sample_n_params(n = max(nrs[[row, 1]] * 0.15, 1), model = model)),
                                       n = as.numeric(nrs[row, 1]),
                                       r = as.numeric(nrs[row, 2]),
                                       s_max = as.numeric(nrs[row, 3]),
                                       max_iter = max_iter,
                                       eta = eta)
    
  }
  
  liszt

}

test_bohb_soft <- bohb_soft(df = data_model, model = "rda") %>% map_dfr(.f = ~ .x[["answer"]])

```

### Hyperband, with hard bayesian opt

```{r}

library(ks)
library(truncnorm)

bohb_hard <- function(df, model, max_iter = 81, eta = 3, bw = 3) {

  logeta = as_mapper(~ log(.x) / log(eta))

  s_max = trunc(logeta(max_iter))

  B = (s_max + 1) * max_iter

  nrs = map_dfc(s_max:0, .f = ~ calc_n_r(max_iter, eta, .x, B)) %>%
    t() %>%
    `colnames<-`(value = c("n", "r")) %>%
    as_tibble()

  nrs$s = s_max:0
  
  random_sh = successive_halving(df = df,
                                 params_config = sample_n_params(n = as.numeric(nrs[1, 1]), model = model),
                                 n = as.numeric(nrs[1, 1]),
                                 r = as.numeric(nrs[1, 2]),
                                 s_max = as.numeric(nrs[1, 3]),
                                 max_iter = max_iter,
                                 eta = eta)
  
  
  #mdl <- random_sh$answer$model[[1]]
  
  length_params <- length(jsons[[model]]$params)
  
  runs_df = random_sh$sh_runs %>%
    distinct() %>%
    arrange(desc(budget), desc(acc)) %>%
    group_by(budget) %>%
    mutate(size = n()) %>%
    ungroup() %>%
    filter(size > length_params * 20/3) %>%
    filter(budget == max(budget)) %>%
    select(-size)
    
  
  liszt = vector(mode = "list",
                 length = max(nrs$s) + 1)
  
  liszt[[1]] <- random_sh
  
  for (row in 2:nrow(nrs)) {
    
    print(nrs[[row, 1]] * 0.7)
    
    print(nrs[[row, 1]] * 0.3)
    
    bayesian_opt_samples = successive_resampling(df = runs_df,
                                                 samples = 256,
                                                 n = round(max(nrs[[row, 1]] * 0.7, 1)),
                                                 bw = bw)
    
    
    current_sh_run = successive_halving(df = df,
                       params_config = bayesian_opt_samples %>% bind_rows(sample_n_params(n = round(max(nrs[[row, 1]] * 0.3, 1)), model = model)),
                       n = nrs[[row, 1]],
                       r = nrs[[row, 2]],
                       s_max = nrs[[row, 3]],
                       max_iter = max_iter,
                       eta = eta)
    
    liszt[[row]] = current_sh_run
    
    runs_df = runs_df %>%
      bind_rows(current_sh_run$sh_run) %>%
      distinct() %>%
      arrange(desc(budget), desc(acc)) %>%
      group_by(budget) %>%
      mutate(size = n()) %>%
      ungroup() %>%
      filter(size > length_params * 20/3) %>%
      filter(budget == max(budget)) %>%
      select(-size)
    
  }
  
  liszt


}


test_bohb_hard <- bohb_hard(df = data_model, model = "boosting") %>% map_dfr(.f = ~ .x[["answer"]])

mult_runs <- microbenchmark::microbenchmark(bohb_hard(df = data_model, model = "boosting", bw = 1.5) %>% map_dfr(.f = ~ .x[["answer"]]),
                                            hyperband(df = data_model, model = "boosting") %>% map_dfr(.f = ~ .x[["answer"]]))

rep_bohb_nobw <- replicate(n = 100, expr = max((bohb_hard(df = data_model, model = "boosting", bw = 1) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))
 
rep_bohb_lowbw <- replicate(n = 100, expr = max((bohb_hard(df = data_model, model = "boosting", bw = 2) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

rep_bohb_highbw <- replicate(n = 100, expr = max((bohb_hard(df = data_model, model = "boosting", bw = 3) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

rep_bohb_highbudgetbw <- replicate(n = 100, expr = max((bohb_hard(df = data_model, model = "boosting", bw = 3, max_iter = 324) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

rep_bohb_highbudgetlowbw <- replicate(n = 100, expr = max((bohb_hard(df = data_model, model = "boosting", bw = 1, max_iter = 324) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))
  
rep_hb <- replicate(n = 100, expr = max((hyperband(df = data_model, model = "boosting") %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

rep_hb_highbudget <- replicate(n = 100, expr = max((hyperband(df = data_model, model = "boosting", max_iter = 324) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

mb <- microbenchmark::microbenchmark(max((bohb_hard(df = data_model, model = "boosting", bw = 1.5) %>% map_dfr(.f = ~ .x[["answer"]]))$acc),
                                     max((hyperband(df = data_model, model = "boosting") %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

#test_bohb_hard <- max((bohb_hard(df = data_model, model = "boosting") %>% map_dfr(.f = ~ .x[["answer"]]))$acc)

## Tests

start <- as.numeric(Sys.time())
duration <- 600
results = NULL
while(as.numeric(Sys.time()) - start < duration) {
  
  results <- c(list(max((bohb_hard(df = data_model, model = "rda") %>% map_dfr(.f = ~ .x[["answer"]]))$acc)), results)
  
}


hb_test <- results %>% flatten_dbl()

hb_hard_small_bw <- results %>% flatten_dbl

hb_hard <- results %>% flatten_dbl()

sh_test <- results

# bohb_hard_test <- replicate(25, expr = max((bohb_hard(df = data_model) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))
# 
# bohb_soft_test <- replicate(25, expr = max((bohb_soft(df = data_model) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))
#   
# hb_test <- replicate(25, expr = max((hyperband(df = data_model) %>% map_dfr(.f = ~ .x[["answer"]]))$acc))

library(hrbrthemes)

accumulated_hb_highbudget <- purrr::accumulate(.x = rep_hb_highbudget, .f = ~ max(.x, .y))

accumulated_hb_highbudgetbw <- purrr::accumulate(.x = rep_bohb_highbudgetbw, .f = ~ max(.x, .y))

accumulated_hb_highbudgetlowbw <- purrr::accumulate(.x = rep_bohb_highbudgetlowbw, .f = ~ max(.x, .y))

accumulated_hb_threebw <- purrr::accumulate(.x = rep_bohb_highbw, .f = ~ max(.x, .y))

accumulate_hb_twobw  <- purrr::accumulate(.x = rep_bohb_lowbw, .f = ~ max(.x, .y))

accumulate_hb_onebw  <- purrr::accumulate(.x = rep_bohb_nobw, .f = ~ max(.x, .y))

accumulate_hb       <- purrr::accumulate(.x = rep_hb, .f = ~ max(.x, .y))

ggplot() +
  geom_line(mapping = aes(x = 1:length(accumulated_hb_highbudgetbw),
                          y = 1 - accumulated_hb_highbudgetbw,
                          color = "High budget and bw")) +
  geom_line(mapping = aes(x = 1:length(accumulated_hb_highbudgetlowbw),
                          y = 1 - accumulated_hb_highbudgetlowbw,
                          color = "High budget and low bw")) +
  geom_line(mapping = aes(x = 1:length(accumulated_hb_highbudget),
                          y = 1 - accumulated_hb_highbudget,
                          color = "High budget Hyperband")) +
  geom_line(mapping = aes(x = 1:length(accumulated_hb_threebw),
                          y = 1 - accumulated_hb_threebw,
                          color = "High bw")) +
  geom_line(mapping = aes(x = 1:length(accumulate_hb_twobw),
                          y = 1 - accumulate_hb_twobw,
                          color = "Small bw")) +
  geom_line(mapping = aes(x = 1:length(accumulate_hb_onebw),
                          y = 1 - accumulate_hb_onebw,
                          color = "No bw")) +
  geom_line(mapping = aes(x = 1:length(accumulate_hb),
                          y = 1 - accumulate_hb,
                          color = "Hyperband")) +
  scale_color_ipsum(name = "Algorithm") +
  theme_ipsum() +
  xlab("Runs") +
  ylab("Regret")
  #scale_x_continuous(breaks = c(1, 122, 422))
  

```

